\documentclass{doc}

\setname{Patrick Hanford}{}
\setmobile{}
\setmail{patrick@phanford.dev}
\setlinkedinaccount{https://linkedin.com/in/phanford}
\setgithubaccount{https://github.com/codespent}
\setwebsite{https://phanford.dev}
\setthemecolor{MidnightBlue}


\begin{document}

%Create header
    \headerview
    \vspace{1ex} % white space
%
    \section{Skills}
    \newcommand{\skillone}{\createskill{Languages}{JavaScript \cpshalf TypeScript \cpshalf Python \cpshalf C\# \cpshalf Go \cpshalf Elixir \cpshalf Kotlin}}
    %
    \newcommand{\skilltwo}{\createskill{Frontend}{React \cpshalf Vue \cpshalf NextJS \cpshalf React Native \cpshalf TailwindCSS}}
    %
    \newcommand{\skillthree}{\createskill{Backend}{Django \cpshalf Flask \cpshalf FastAPI \cpshalf Entity Framework \cpshalf GraphQL}}
    %
    \newcommand{\skillfour}{\createskill{Cloud/DevOps}{AWS \cpshalf GCP \cpshalf Azure \cpshalf Docker \cpshalf GitHub Actions}}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour}
    \vspace{-3mm} % reduces whitespace!
    %
%
    \section{Experience}
    %
    \datedexperience{Ford Motors International}{Sep 2024 - Nov 2025}
    \explanation{Fullstack Software Engineer}{}
    \explanationdetail{
        \smallskip
        \coloredbullet\ %
        Worked with data engineers to integrate new data sources across the company domain into generative AI products, increasing the user-base.

        \smallskip
        \coloredbullet\ %
        Integrated internal API analytics product into generative AI products to identify actionable insights in performance, reducing average response time by ~90\% (1m14s to 7.2s).

        \smallskip
        \coloredbullet\ %
        Built a Text2SQL integration into the generative AI product from scratch as an independent service, creating a completely new customer base.

        \smallskip
        \coloredbullet\ %
        Built Chart.js integration into LLM response components, enabling dynamic data visualization from RAG outputs, replacing static table displays.

        \smallskip
        \coloredbullet\ %
        Developed async dynamic dropdown components with incremental API loading, adopted as common components across the micro-UI ecosystem.

        \smallskip
        \coloredbullet\ %
        Optimized RAG pipeline APIs (Flask/FastAPI), added new data sources, reduced response time by 90\% (1m14s to 7.2s), and scaled architecture for increasing payload demands.

        \smallskip
        \coloredbullet\ %
        Added dynamic functionality to common UI components to support more advanced use cases such as dynamic options loading, virtual scroll, and emitters.

        \smallskip
        \coloredbullet\ %
        Implemented DX (developer experience) standards and policies to aid team productivity and streamline feature development with less regression and conflicts.

        \smallskip
        \coloredbullet\ %
        Supported production deployment of an internal tool built to replace a legacy system used company-wide for data aggregations.

        \bigskip
    }
    %
    \datedexperience{Robert Half International}{Feb 2020 - Mar 2024}
    \explanation{Fullstack Software Engineer}{}
    \explanationdetail{
        \smallskip
        \coloredbullet\ %
        Implemented Docker Swarm for an agency supporting numerous legacy Laravel (PHP) sites.

        \smallskip
        \coloredbullet\ %
        Redesigned an Angular Cordova cross-platform mobile application for React Native, managing app store compliances and distribution pipelines.

        \smallskip
        \coloredbullet\ %
        Developed DotNet Core (C\#) API for a mobile application using Entity Framework, Linq, and SQL Server.

        \smallskip
        \coloredbullet\ %
        Designed a system to maintain data across multiple databases (SQL Server, Postgres, MySQL) using the Serenity framework (C\#).

        \smallskip
        \coloredbullet\ %
        Extended and maintained CI/CD pipelines for various app types in Azure DevOps, GitHub Actions, AWS Elastic Beanstalk, and Jenkins.

        \smallskip
        \coloredbullet\ %
        Developed a video conferencing application using Django Rest Framework (Python) and NextJS (React).

        \bigskip
    }
%
    \section{Notable Projects}
    %
    \datedexperience{TakePoint (takepoint.dev)}{}
    \explanation{AI-Enhanced Sprint Planning Platform}{}
    \explanationdetail{
        \smallskip
        \coloredbullet\ %
        Built a full-stack application with React frontend and Python backend in Yarn-managed monorepo, deployed to AWS via CloudFormation IaC.

        \smallskip
        \coloredbullet\ %
        Integrated OpenAI API with RAG strategies to generate real-time insights during sprint planning and retrospective sessions.

        \smallskip
        \coloredbullet\ %
        Built bi-directional syncing of Stories and Action Items for Jira and similar platforms to create end-to-end workflows.

        \smallskip
        \coloredbullet\ %
        Implemented cost optimization strategies reducing OpenAI API usage by 46\% while maintaining response quality through prompt engineering and caching.

        \smallskip
        \coloredbullet\ %
        Conducted private user testing with 4 agile teams, incorporating feedback to refine story pointing and retrospective workflows.

        \smallskip
        \coloredbullet\ %
        Containerized application with Docker and built self-hosted deployment option for enterprise clients with data privacy concerns.

        \smallskip
        \coloredbullet\ %
        Integrated Stripe with webhooks for seamless subscription management.

        \smallskip
        \textit{Python, TypeScript, PostgreSQL, MongoDB, CloudFormation, TensorFlow, OpenAI, Stripe, Jira, AWS, Docker, GitHub Actions}

    }
\end{document}
